Explosive information of terrorism is altering public opinion

### 2024-02-15 output/paper/paper.qmd
fixing type

In this study, I will replicate the study and figures of @main. Based on Godefroidt's publication, I will explore the different degrees of the effect on political attitude originated from terrorism in different countries and time in the history. In @sec-data, I will introduce the dataset used in this study. All of the data are obtained from the replication package provided by Godefroidt. After explaining in detail about the data collection procedure of the original paper regarding the meta-analysis, I will discuss the data procession methods in both the original paper and the following part of this study. Then, I will proceed to the result part in @sec-result. I will introduce the major and key result of the orginial paper found by @main. Then, I will dive deeper in explaning the differences of such effect by countries and its changing trend over time. Finally, in @sec-discussion, I impose three major questions after the replication of the article. I also include a discussion of limitation of this study, along with the expectation of future study.

@@

## Meta analysis data visualization
### Year to study categorized by country
In the original paper, @main shows that the start year of research in terrorism and public opinion has a general increase trend after it bursted out after the 9/11 event in 2001. The author also shows how this number peaks at specific terrorist attack event, such as train bombing in Madrid in 2004 and the massive terror attack in Paris in 2015. However, @fig-country explains the story in a more specific and detailed way. Regarding the number, the US conducted the most research for papers and reports in studying terrorism and public opinion. Among the total 541 research done in the US, a total of 94 researches started data collection procedure in 2001 after the 9/11 event alone. The second most country is Israel with a total of 415 research conducted. Unlike US, many of the research conducted by Israel scientists use data before major events. Additionally, there is no substantial peak. The busrt of studies in Israel are correlated with all major events of terrorist attack. The situation in Spain and France are simiar. They all have a obvious peak when a severe terrorist event happened in the border. 37 out of the total 60 studies started in 2004 after the Madrid Bombing attack in Spain, and 58 out of the total 68 studies started in 2015 after the IS attack in France. UK has conducted a total of 77 studies in this field since 2002. Comparatively, Canada is involved in this topic the least among the six countries, which only has 16 studies.

@@

### Type of terrorism over years
@main calculates and presents the probability of different types of terrorism in the meta-analysis data. In the data visualization part, the author shows that over 60% of terrorism studied is Islamic terrorism, much more than all other types. The second largest group, no ideology studies, only consist about 20% of total research. However, the author only examines the probability of the total number in different types without a detailed examination of change regarding time. Much information is still hidden under the original bar chart. @fig-type, on the other hand, is more comprehensive and uncovers the changing interest of political scientists in specific topics. Echoing with @main, studies regarding Islamic type of terrorism is always the most except for 2005. Though the no ideology type of studies is almost as many as Islamic type, the porportion of Islamist surged after 2015. In addition to traditional topics, the extreme right type is so young that it has not appeared until 2016. This type of study is rapidly growing, from only 1 in 2016 to 6 in 2019.

@@

In the original study, @main adoped a three-level approach to study the effect size of three specific categories: outgroup Hostility, conservative shift, and rally effect. Initially, the meta analysis will only provide the effect size of manuscripts with three error terms: a deviation of the mean population effect size in specific manuscript from overall population effect size; a deviation population effect size regard another manuscript from the mean effect in its own, and a error term due to sampling fluctuation. @main then extends to build an extensive model where dependent variables could be a specific charateristic $(X_j)$ that we would like to study and effect size within manuscripts $(X_{ij})$. The model can be written as:
\begin{equation*}
Y_{ij} = \beta_0 + u_{(2)ij} + u_{(3)j} + e_{ij},
\end{equation*}

I adopt the same model for the following discussion in this study. To be more specific, I will also examine the regressional relationship on the observed effective size of manuscriipt by making a characteristic of the manuscript from the columns of meta-analysis data as a dummy variable. However, I wil emphasize the effect of terrorism in differen geographic area. Thus, the "Country" information in the data is the major variable studied.

@@

The article then explores moderators of the relationship between terrorism and political attitudes, revealing substantial heterogeneity in effect sizes. By assigning interested columns into dummy varaibles, @main finds out that many methodological factors, including study design and timing of measurements, also affect observed effect sizes. Among all of the factors, a notable finding is that studies on non-Islamist terrorism yield weaker or nonsignificant correlations, which implies the biased social psychology regarding the Islamic group.

@@

Terrorism has risen to be a global concern for a long time. New York, Madrid, Paris and many world first class metropolitan cities have witnessed the attack of terrorists. Hundreds and thousands of injuries and casualties are directly of indirectly caused by terrorism.The growing power of the terrorist groups require a global act to defend together.[@lafree2014putting] However, the findings of literature shows an extremely narrow perspective where citizens highlight national securities after explosive to massive information of terrorism.[@lafree2014putting] More importantly, historical literatures are biased in geography themselves.

The findings presented in the meta-analysis data and its analysis of @fig-country suggest a nationalistic approach towards the study of terrorism, where the focus predominantly lies within the borders of the researchers' own countries. The surge in research post major terrorist events, such as the 9/11 attacks in the United States or the Madrid bombings, indicates a reactionary stance in academia, which largely aligns with immediate national concerns rather than a unified global effort against terrorism. The U.S. and Israel lead in the volume of research conducted, reflecting their direct engagement with significant terrorist activities. Spain and France, on the other hand, only conduct large amount of research when severe attack occured in their home country. Many other countries that are lucky enough that they have not experience direct attack from terrorists are not even included in the meta analysis. This national-centric view may hinder the development of comprehensive strategies that address the root causes of terrorism and foster international collaboration.

@@

The limitation of this study is generated from the meta-analysis procedure and the consequent dataset. Firstly, the collection of dataset is done by the author Amélie Godefroidt, which may induce personal bias due to assymetric information. Though the author adopts certain procedures and methods to prevent such bias, it is nevitable to have bias of omitting studies that is not accessible for the author. One possible reason is that the paper was written in other languages than English. Secondly, the effect size calculation is based on mannual adjustment of associations in distinctive papers by Godefroidt. Personal understanding of the paper may also generate biad to the intepretation of the models in meta-analysis dataset. Thirdly, the result part emphasizes on only 6 countries that I picked, partly due to personal interest. This may not reveal a comprehensive illustration of the effect of terrorism all over the world.

## Future study
Based on the questions I proposed in the discussion part, future study of terrorism and the effect on general political attitude alternations should adopt a globalized horizon. Comparing the magnitute of mind changing between citizens who live in the country which is directly attacked by terrorist groups and those who do not may be a method to explore the effect of terrorism in social psychology.

>>>>

In this study, I will replicate the study and figures of @main. Based on Godefroidt's publication, I will explore the different degrees of the effect on political attitude originated from terrorism in different countries and time in the history. In @sec-data, I will introduce the dataset used in this study. All of the data are obtained from the replication package provided by Godefroidt. After explaining in detail about the data collection procedure of the original paper regarding the meta-analysis, I will discuss the data procession methods in both the original paper and the following part of this study. Then, I will proceed to the result part in @sec-result. I will introduce the major and key result of the original paper found by @main. Then, I will dive deeper in explaining the differences of such effect by countries and its changing trend over time. Finally, in @sec-discussion, I impose three major questions after the replication of the article. I also include a discussion of limitation of this study, along with the expectation of future study.

@@

## Meta analysis data visualization
### Year to study categorized by country
In the original paper, @main shows that the start year of research in terrorism and public opinion has a general increase trend after it busted out after the 9/11 event in 2001. The author also shows how this number peaks at specific terrorist attack event, such as train bombing in Madrid in 2004 and the massive terror attack in Paris in 2015. However, @fig-country explains the story in a more specific and detailed way. Regarding the number, the US conducted the most research for papers and reports in studying terrorism and public opinion. Among the total 541 research done in the US, a total of 94 researches started data collection procedure in 2001 after the 9/11 event alone. The second most country is Israel with a total of 415 research conducted. Unlike US, many of the research conducted by Israel scientists use data before major events. Additionally, there is no substantial peak. The burst of studies in Israel are correlated with all major events of terrorist attack. The situation in Spain and France are similar. They all have a obvious peak when a severe terrorist event happened in the border. 37 out of the total 60 studies started in 2004 after the Madrid Bombing attack in Spain, and 58 out of the total 68 studies started in 2015 after the IS attack in France. UK has conducted a total of 77 studies in this field since 2002. Comparatively, Canada is involved in this topic the least among the six countries, which only has 16 studies.

@@

### Type of terrorism over years
@main calculates and presents the probability of different types of terrorism in the meta-analysis data. In the data visualization part, the author shows that over 60% of terrorism studied is Islamic terrorism, much more than all other types. The second largest group, no ideology studies, only consist about 20% of total research. However, the author only examines the probability of the total number in different types without a detailed examination of change regarding time. Much information is still hidden under the original bar chart. @fig-type, on the other hand, is more comprehensive and uncovers the changing interest of political scientists in specific topics. Echoing with @main, studies regarding Islamic type of terrorism is always the most except for 2005. Though the no ideology type of studies is almost as many as Islamic type, the proportion of Islamist surged after 2015. In addition to traditional topics, the extreme right type is so young that it has not appeared until 2016. This type of study is rapidly growing, from only 1 in 2016 to 6 in 2019.

@@

In the original study, @main adopted a three-level approach to study the effect size of three specific categories: outgroup Hostility, conservative shift, and rally effect. Initially, the meta analysis will only provide the effect size of manuscripts with three error terms: a deviation of the mean population effect size in specific manuscript from overall population effect size; a deviation population effect size regard another manuscript from the mean effect in its own, and a error term due to sampling fluctuation. @main then extends to build an extensive model where dependent variables could be a specific characteristic $(X_j)$ that we would like to study and effect size within manuscripts $(X_{ij})$. The model can be written as:
\begin{equation*}
Y_{ij} = \beta_0 + u_{(2)ij} + u_{(3)j} + e_{ij},
\end{equation*}

I adopt the same model for the following discussion in this study. To be more specific, I will also examine the regression relationship on the observed effective size of manuscript by making a characteristic of the manuscript from the columns of meta-analysis data as a dummy variable. However, I will emphasize the effect of terrorism in different geographic area. Thus, the "Country" information in the data is the major variable studied.

@@

The article then explores moderators of the relationship between terrorism and political attitudes, revealing substantial heterogeneity in effect sizes. By assigning interested columns into dummy variables, @main finds out that many methodological factors, including study design and timing of measurements, also affect observed effect sizes. Among all of the factors, a notable finding is that studies on non-Islamist terrorism yield weaker or non significant correlations, which implies the biased social psychology regarding the Islamic group.

@@

Terrorism has risen to be a global concern for a long time. New York, Madrid, Paris and many world first class metropolitan cities have witnessed the attack of terrorists. Hundreds and thousands of injuries and casualties are directly of indirectly caused by terrorism.The growing power of the terrorist groups require a global act to defend together.[@lafree2014putting] However, the findings of literature shows an extremely narrow perspective where citizens highlight national securities after explosive to massive information of terrorism.[@lafree2014putting] More importantly, historical literature are biased in geography themselves.

The findings presented in the meta-analysis data and its analysis of @fig-country suggest a nationalistic approach towards the study of terrorism, where the focus predominantly lies within the borders of the researchers' own countries. The surge in research post major terrorist events, such as the 9/11 attacks in the United States or the Madrid bombings, indicates a reactionary stance in academia, which largely aligns with immediate national concerns rather than a unified global effort against terrorism. The U.S. and Israel lead in the volume of research conducted, reflecting their direct engagement with significant terrorist activities. Spain and France, on the other hand, only conduct large amount of research when severe attack occurred in their home country. Many other countries that are lucky enough that they have not experience direct attack from terrorists are not even included in the meta analysis. This national-centric view may hinder the development of comprehensive strategies that address the root causes of terrorism and foster international collaboration.

@@

The limitation of this study is generated from the meta-analysis procedure and the consequent dataset. Firstly, the collection of dataset is done by the author Amélie Godefroidt, which may induce personal bias due to asymmetric information. Though the author adopts certain procedures and methods to prevent such bias, it is inevitable to have bias of omitting studies that is not accessible for the author. One possible reason is that the paper was written in other languages than English. Secondly, the effect size calculation is based on manual adjustment of associations in distinctive papers by Godefroidt. Personal understanding of the paper may also generate bias to the interpretation of the models in meta-analysis dataset. Thirdly, the result part emphasizes on only 6 countries that I picked, partly due to personal interest. This may not reveal a comprehensive illustration of the effect of terrorism all over the world.

## Future study
Based on the questions I proposed in the discussion part, future study of terrorism and the effect on general political attitude alternations should adopt a globalized horizon. Comparing the magnitude of mind changing between citizens who live in the country which is directly attacked by terrorist groups and those who do not may be a method to explore the effect of terrorism in social psychology.
